---
title: "Project-1"
author: "Ayo"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the packages 
```{r}
library(tidyverse)
library(skimr)
```

## Reading the dataset

```{r}
df <- read.csv('book_reviews.csv')
```

## Assessing the dataframe 
```{r}
dim(df)
```

```{r}
colnames(df)
```
## check the datatypes 
```{r}
for (col in colnames(df)) {
  print(class(df[[col]]))
  }
```

## Checking the distinct values 
```{r}

for (col in colnames(df)) {
  print(col)
  print(unique(df[[col]]))
}

table(df$review)
```
```{r}
new_df <- df %>% 
  filter(!is.na(review))
```

## Cleaning the dataset

```{r}
clean_df <- new_df %>% 
  mutate(
    state = case_when(
      state == 'California' ~ 'CA',
      state == 'New York' ~ 'NY',
      state == 'Texas' ~ 'TX',
      state == 'Florida' ~ 'FL',
      TRUE ~ state
    )
  )
```

```{r}
clean_df <- clean_df %>%
  mutate(
    review_num = case_when(
      review == "Poor" ~ 1,
      review == "Fair" ~ 2,
      review == "Good" ~ 3,
      review == "Great" ~ 4,
      review == "Excellent" ~ 5
      ),
    high_review = if_else(review_num >= 4, TRUE, FALSE)

)

```

# Objective of analysis 
## What book is the most profitable book
## The most purchased book

```{r}
clean_df %>% 
  group_by(book) %>% 
  summarise(revenue = sum(price)) %>% 
  arrange(-revenue)
```

```{r}
clean_df %>% 
  group_by(book) %>% 
  summarise(sold = n()) %>%
  arrange(-sold)

```
Here we see the highest sold books is Fundamental of R For Beginners 

## Data visualization
```{r, fig.width=15, fig.height=10}
library(ggplot2)
analysis <- clean_df %>% 
  group_by(book) %>% 
  summarise(revenue = sum(price)) %>% 
  arrange(-revenue) %>% 
  ggplot(aes(x=book, y=revenue, fill=book)) + geom_col(position = 'dodge') + 
  labs(title = "Total sold price per books",
       subtitle = 'This shows the total price all the books sold', 
       x= "Books", 
       y= 'Total sold price', 
       caption= "Data from dataquest class") + theme(axis.text.x = element_blank()) 
```

```{r}
analysis <- analysis + scale_fill_brewer(palette="Set2") + theme(legend.position = 'bottom') 
analysis
```

From the result above we can see that the most profitable book is secrets of R for Advanced students 
